Quotient Normalized Maximum Likelihood Criterion for Learning Bayesian Network Structures

### 2017-03-26 bn.tex
something on BDeu irregularity

>>>>

Recently, Suzuki~\cite{Suzuki2017} discussed the theoretical properties of the BDeu of score and showed that in certain settings BDeu has tendency to add more and more parent variables for a child node even though the empirical conditional entropy of the child given the parents has already reached zero. More in detail, assume that in our data $D$, the values of $X_i$ are completely determined by variables in set $Z$, so that the entropy $H(X | Z) = 0$. Now, if we can further find one or more variables, denoted by $Y$, whose values are determined completely by the variables in $Z$, then BDeu will prefer the set $Z\cup Y$ over mere $Z$ as the parents of $X_i$. Suzuki argues that this kind of behaviour violates regularity in model selection as the more complex model is preferred over a simpler one even though it does not fit to data any better. The phenomena seems to stem from the way the hyperparameters for the Dirichlet distribution are chosen in BDeu as the  BD score based on the Jeffreys prior does not suffer from this anomaly.
